A Formal Model of Checked C

### 2023-01-17 sandp23/evaluation.tex
Adding al

@@

>>>>

We ensured that the partitioned programs retained their expected functionality by verifying using corresponding test suites.

@@

\subsection{Security Impact}
\label{subsec:securityimpact}
The last column of~\tbl{TODO} shows the list of all spatial safety vulnerabilities in the functions that have tainted types or are isolated in the~\ucregion{}.
As expected,~\emph{all vulnerabilities} are prevented by~\systemname{}.
The symbols~\vulprevented{} and~\vulisolated{} indicate whether the vulnerability was detected by our dynamic instrumentation or isolated in the sandbox, respectively.
This shows that~\systemname{} provides an effective mechanism to prevent spatial safety vulnerabilities.

\aravind{Fix the conversion effort table by the correct symbols}
